SAT Competition 2020\tnoteref{title}

### 2021-06-05 paper/main.tex
fixed all solver-names reaching into margin

Four solvers participating in the Main track, namely \solver{Kissat-sat}, \solver{Relaxed-newTech}, \solver{CaDiCaL-alluip-trial}, and \solver{CMS-ccnr-lsids},
performed significantly better that all other solvers submitted to the Main track, see Table~\ref{tab:results}.
Figure~\ref{main:all} shows the cumulative solved instances plot of the best-performing solver of the strongest
10 teams (in short, the top-10 solvers)  together with the Virtual Best Solver (VBS---see also~\ref{subsec:vbs_explained}).
The four top solvers all have a different code base, which is rare and has not been observed for many years.
Also, in recent competitions, the top solvers were much closer to each other in terms of runtime performance.
The winning solver is \solver{Kissat-sat} and the runner-up is \solver{Relaxed-newTech}. Notice that 
\solver{Relaxed-newTech} solved more instances within the 2000-second limit.
Third place, based on the PAR-2 score, went to \solver{CMS-ccnr-lsids}. It solved two fewer instances
compared to \solver{CaDiCaL-alluip-trial}, but solved various formulas much more quickly. 
Since the SAT Competition nowadays applies the PAR-2 score for ranking solvers, such cases have been observed several times.

@@

Overall, solvers performed much more similarly on
unsatisfiable formulas,
see Figure~\ref{main:unsat}. Only \solver{Kissat-unsat}, the winner of the Main UNSAT track, 
performed significantly better compared to all other participants. It is therefore not surprising
that the VBS is reasonably close to \solver{Kissat-unsat}. \solver{Kissat} is a new solver that has been implemented in C, while most solvers are implemented in C++. Further 
details about \solver{Kissat} are given in Section~\ref{sec:kissat}.
The solvers \solver{CaDiCaL-trial}
and \solver{f2trc-s} placed, respectively, second and third in the Main UNSAT track.

@@

The competition in the Planning Track was more tight. \solver{CaDiCaL-alliup-trial}, the winning solver, 
solved only one instance more compared to the runner up \solver{CMS-ccnr-lsids}. Their PAR-2 score is 
quite close as well. The third ranked solver, \solver{Kissat}, solved fewer instances, but its fast runtimes
on several instances resulted in a strong PAR-2 score. Notice that these three solvers were also strong in the Main track. 
Apparently none of the participating solvers was optimized for planning instances.

@@

\solver{Painless-MCOMSPS-STR} diversifies mainly via hard-coded configurations of the branching strategies LRB and VSIDS, and via sparse random initialization of variable polarities~\cite{Balyo:2015:HordeSATs}. 
Two special solver instances perform concurrent clause strengthening~\cite{Wieringa:2013:CCS} and Gaussian elimination, respectively. 
\solver{Painless-MCOMSPS-STR} uses an all-to-all strategy for clause sharing with a fixed-size clause buffer and an LBD filter with a dynamic limit~\cite{SC2020}.

>>>>

The four solvers \solver{Kissat-sat}, \solver{Relaxed-newTech}, \solver{CaDiCaL-alluip-trail}, and \solver{CMS-ccnr-lsids} performed significantly better that all other solvers submitted to the Main track (cf. Table~\ref{tab:results}).
Figure~\ref{main:all} shows the cumulative solved instances plot of the best-performing solver of the strongest
10 teams (in short, the top-10 solvers)  together with the Virtual Best Solver (VBS---see also~\ref{subsec:vbs_explained}).
The four top solvers all have a different code base, which is rare and has not been observed for many years.
Also, in recent competitions, the top solvers were much closer to each other in terms of runtime performance.
The winning solver is \solver{Kissat-sat} and the runner-up is \solver{Relaxed-newTech}. Notice that 
\solver{Relaxed-newTech} solved more instances within the 2000-second limit.
Third place, based on the PAR-2 score, went to \solver{CMS-ccnr-lsids}. It solved two fewer instances
compared to \solver{CaDiCaL-alluip-trail}, but solved various formulas much more quickly. 
Since the SAT Competition nowadays applies the PAR-2 score for ranking solvers, such cases have been observed several times.

@@

Overall, solvers performed much more similarly on
unsatisfiable formulas,
see Figure~\ref{main:unsat}. Only \solver{Kissat-unsat}, the winner of the Main UNSAT track, 
performed significantly better compared to all other participants. It is therefore not surprising
that the VBS is reasonably close to \solver{Kissat-unsat}. \solver{Kissat} is a new solver that has been implemented in C, while most solvers are implemented in C++. Further 
details about \solver{Kissat} are given in Section~\ref{sec:kissat}.
The solvers \solver{CaDiCaL-trail}
and \solver{f2trc-s} placed, respectively, second and third in the Main UNSAT track.

@@

The competition in the Planning Track was more tight. The winning solver \solver{CaDiCaL-alliup-trail} solved only one instance more compared to the runner up \solver{CMS-ccnr-lsids}. 
Their PAR-2 score is 
quite close as well. The third ranked solver, \solver{Kissat}, solved fewer instances, but its fast runtimes
on several instances resulted in a strong PAR-2 score. Notice that these three solvers were also strong in the Main track. 
Apparently none of the participating solvers was optimized for planning instances.

@@

\solver{Painless-MCOMSPS-STR} diversifies mainly via hard-coded configurations of the branching strategies LRB and VSIDS, and via sparse random initialization of variable polarities~\cite{Balyo:2015:HordeSATs}. 
Two special solver instances perform concurrent clause strengthening~\cite{Wieringa:2013:CCS} and Gaussian elimination, respectively. 
Regarding sharing, \solver{Painless-MCOMSPS-STR} uses an all-to-all strategy with a fixed-size clause buffer and an LBD filter with a dynamic limit~\cite{SC2020}.
